\documentclass{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{amssymb,amsfonts,amsmath,amsthm}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{listings}
\usepackage{enumerate}
\usepackage{float}
\usepackage{fullpage}

\newcommand{\e}{\mathrm{e}}
\newcommand{\der}{\mathrm{d}}
\newcommand{\Ne}{N_\mathrm{e}}
\newcommand{\SetCodon}{\Omega_{\mathrm{C}}}
\newcommand{\SetNuc}{\Omega_{\mathrm{N}}}
\newcommand{\SetWeak}{\Omega_{\mathrm{W}}}
\newcommand{\SetStrong}{\Omega_{\mathrm{S}}}
\newcommand{\SetAa}{\Omega_{\mathrm{A}}}
\newcommand{\Neighbor}{\mathcal{V}}
\newcommand{\NonSyn}{\mathcal{N}}
\newcommand{\Syn}{\mathcal{S}}
\newcommand{\Nx}{\Neighbor_x}
\newcommand{\NxAB}{\Neighbor_x^{\mathrm{A} \rightarrow \mathrm{B}}}
\newcommand{\NyBA}{\Neighbor_x^{\mathrm{B} \rightarrow \mathrm{A}}}
\newcommand{\NxWS}{\Neighbor_x^{\mathrm{W} \rightarrow \mathrm{S}}}
\newcommand{\NxSS}{\Neighbor_x^{\mathrm{S} \rightarrow \mathrm{S}}}
\newcommand{\NxSW}{\Neighbor_x^{\mathrm{S} \rightarrow \mathrm{W}}}
\newcommand{\NxWW}{\Neighbor_x^{\mathrm{W} \rightarrow \mathrm{W}}}
\newcommand{\NyWS}{\Neighbor_y^{\mathrm{W} \rightarrow \mathrm{S}}}
\newcommand{\NySS}{\Neighbor_y^{\mathrm{S} \rightarrow \mathrm{S}}}
\newcommand{\NySW}{\Neighbor_y^{\mathrm{S} \rightarrow \mathrm{W}}}
\newcommand{\NyWW}{\Neighbor_y^{\mathrm{W} \rightarrow \mathrm{W}}}
\newcommand{\NxNonSyn}{\NonSyn_x}
\newcommand{\NyNonSyn}{\NonSyn_y}
\newcommand{\NxSyn}{\Syn_x}
\newcommand{\NySyn}{\Syn_y}

% \renewcommand{\baselinestretch}{2}

\author{Thibault Latrille.}
\title{Notes }

\begin{document}

    \maketitle

    \section*{Abstract}


    \tableofcontents
    \newpage

    \section{Phylogenetic}
	Selectively neutral and positively selected mutations contribute to divergence. On the other hand negatively selected mutations (weak and strong) are purged.
	
	Assumptions : 
	\begin{itemize}
		\item Identically fitness landscape for each site (can be relaxed) 
		\item Static effective population size (can be relax)
		\item No epistasis, independence between sites (hard to relax)
		\item Static fitness landscape (hard to relax)
	\end{itemize}
	
	Sensitive to assumption of no epistasis and static fitness landscape, unfortunately these are hard to relax.
	\section{Population-genetic}
	Selectively neutral and weakly selected (positively and negatively). Strongly selected mutations don't contribute to the data.
	
	Assumptions : 
	\begin{itemize}
		\item Identically fitness landscape for each site (can be relaxed) 
		\item Static effective population size (can be relax)
		\item No epistasis, independence between sites (hard to relax)
		\item Static fitness landscape (hard to relax)
	\end{itemize}
	
	Less sensitive to assumption of no epistasis and static fitness landscape. The first strategy is to augment information about interspecies conservation with information about genetic polymorphism.
	
	\section{Population-phylogenetic}
	
	The shorter evolutionary time scales associated with intraspecies variation make this approach more robust to changing fitness landscape and less sensitive to errors in alignment and orthology detection. 
	
    \section{Epistasis}
   
    \section{Changing fitness landscape}
    
    
\end{document}
